---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
library(ggplot2)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
  #,out.width = "400px"
)
```
# graphhopper-R

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/graphhopper)](https://CRAN.R-project.org/package=graphhopper)
[![Travis build status](https://travis-ci.org/crazycapivara/graphhopper-r.svg?branch=master)](https://travis-ci.org/crazycapivara/graphhopper-r)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
<!-- badges: end -->

An R Interace to [GraphHopper](https://www.graphhopper.com/) APIs

The purpose of {graphhopper} is to provide a quick and easy access to GraphHopper
APIs. You can easily convert responses to simple feature (sf) objects.

## Installation

Install the release version from [CRAN](https://cran.r-project.org/) with:

```r
install.packages("graphhopper")
```

Install the development version from [GitHub](https://github.com/) with:

```r
# install.packages("remotes")
remotes::install_github("crazycapivara/graphhopper-r")
```

## Get started

Run your own GraphHopper instance (with data of Berlin):

```bash
docker run --name gh --rm -p 8989:8989 -d graphhopper/graphhopper:2.0
```

### Setup

```{r example}
library(graphhopper)

API_URL <- "http://localhost:8989"
gh_set_api_url(API_URL)

info <- gh_get_info()

info$version
info$data_date
gh_bbox(info)
```

### Route

Get a route in Berlin:

```{r route-example}
start_point <- c(52.592204, 13.414307)
end_point <- c(52.539614, 13.364868)

(route <- gh_get_route(list(start_point, end_point)) %>%
    gh_as_sf())

ggplot(data = route) +
  geom_sf() +
  theme(axis.text.x = element_text(angle = 45))

route$time

via_point <- c(52.545461, 13.435249)

route2 <- gh_get_route(list(start_point, via_point, end_point))

gh_time_distance(route2)

ggplot(data = gh_as_sf(route2)) +
  geom_sf() +
  theme(axis.text.x = element_text(angle = 45))

gh_points(route2) %>%
  head()

gh_instructions(route2)[, c("lon", "lat", "gh_id", "gh_end_id", "text", "distance")] %>%
  head()
```

### Shortest path tree

```{r spt-example}
start_point <- c(52.53961, 13.36487)

points_sf <- gh_get_spt(start_point, time_limit = 180) %>%
  gh_as_sf() %>%
  dplyr::mutate(time = (time / 1000 / 60))

ggplot() +
  geom_sf(data = points_sf, aes(colour = time), size = 0.5) +
  theme(axis.text.x = element_text(angle = 45))
```

Also query previous nodes to plot the network:

```{r spt-example-lines}
(columns <- gh_spt_columns(
  prev_longitude = TRUE,
  prev_latitude = TRUE,
  prev_time = TRUE
))

lines_sf <- gh_get_spt(end_point, time_limit = 240, columns = columns) %>%
  dplyr::mutate(mean_time = ((time + prev_time) / 2) / 1000 / 60) %>%
  gh_spt_as_linestrings_sf()

ggplot() +
  geom_sf(data = lines_sf, aes(color = mean_time), size = 1) +
  theme(axis.text.x = element_text(angle = 45))
```
